% Shortcuts for Canary information incorporated in multiple versions of manuals
%
% This file is includeded in all top-level .tex files

% When using this command, likely follow with a forced space, e.g., one of
% Version \CanaryVersion\ Manual
% Version \CanaryVersion\space Manual
% Version \CanaryVersion{} Manual
\newcommand{\CanaryVersion}{5.0}
%%\newcommand{\CanaryVersion}{5.0+}


% Most recent SAND report numbers and report date based on
% Data should be SAND report date and not reflect updates
\newcommand{\CanarySANDDate}{December 2009}
\newcommand{\CanarySANDDev}{SAND2010-2185}
\newcommand{\CanarySANDRef}{SAND2010-2184}
\newcommand{\CanarySANDUsers}{SAND2010-2183}
\newcommand{\CanarySANDTheory}{SAND2011-9106}


% Need to manually break line or Eldred gets incorrectly split
\newcommand{\CanaryAuthorSAND}{
David~B.~Hart, Nathanael~P.~Rackley
}

\newcommand{\CanaryAuthorLong}{
David~B.~Hart, Nathanael~P.~Rackley\\
Geochemistry Department\\
\\
Sandia National Laboratories\\
P.O. Box 5800\\
Albuquerque, NM 87185
}

\newcommand{\CanaryAuthorFormatted}{
{\large \bf David B. Hart, Nathanael P. Rackley}\\ 
{\large Geochemistry Department}\\
\vspace*{0.5cm}
{\large Sandia National Laboratories}\\
{\large P.O. Box 5800}\\
{\large Albuquerque, New Mexico 87185}\\
}


% Fragments which together comprise abstracts

\newcommand{\CanaryAbstractShared}{

% blank line intended

% blank line intended
}

\newcommand{\CanaryAbstractDev}{
This report serves as a developers manual for the Canary software and
describes the Canary class hierarchies and their interrelationships.
It derives directly from annotation of the source code and provides
detailed class documentation, including all member functions and
attributes.  
}

\newcommand{\CanaryAbstractRef}{
This report serves as a reference manual for the commands specification
for the Canary software, providing input overviews, option descriptions,
and example specifications.
}

\newcommand{\CanaryAbstractUsers}{
This report serves as a user's manual for the Canary software and
provides capability overviews and procedures for software execution,
as well as a variety of example studies.
}

\newcommand{\CanaryAbstractTheory}{
This report serves as a theoretical manual for selected algorithms
implemented within the Canary software.
}

\newcommand{\SandiaFundingStatement}{
Sandia National Laboratories is a multi-program laboratory managed and operated by 
Sandia Corporation, a wholly owned subsidiary of Lockheed Martin Corporation, for
the U.S. Department of Energy’s National Nuclear Security Administration under 
contract DE\-AC04\-94AL85000.
}

\newcommand{\CanaryAcknowledge}{
The U.S. Environmental Protection Agency (EPA) through its Office of Research and Development
funded and collaborated in the development of CANARY-EDS under an Inter-Agency Agreements
with the Department of Energy's Sandia National laboratories 
(IAG numbers DW8992192801, DW8992368101).

Additionally, the authors would like to thank the following members of the EPA's National Homeland
Security Research Center for their help in testing the new version of
the software: Jonathan Burkhardt, John Hall, Terra Haxton, and Regan Murray.
}
